### 2019-04-05 _publications/jors/paper.tex
Update for tkphd review

PFHub is a community effort spearheaded by the Center for Hierarchical
Materials Design at Northwestern University and the National Institute
of Standards and Technology in support of phase-field code
development. The current PFHub deployment~\cite{pfhub} focuses on
improving cross-collaboration between phase-field code developers and
practitioners by providing a standardized set of benchmark
problems~\cite{bm1, bm2} and a workflow for uploading and comparing
benchmark results from different phase-field codes (\emph{e.g.},
MOOSE~\cite{moose}, PRISMS-PF~\cite{prisms-pf}, FiPy~\cite{fipy},
MMSP~\cite{mmsp}).

@@

The PFHub framework provides a template for other small scientific
communities to host custom content and integrate data from members of
their community. The current deployment provides a facility for
uploading, displaying and comparing results from benchmark problems
supporting phase-field code developers and practitioners. However, the
framework and overall philosophy are broadly transferable to other
communities with some custom configuration and content generation. The
framework uses the Jekyll~\cite{jekyll} static website
generator~\cite{jekyll} along with automated front-end processing to
eliminate the need for a CMS~\cite{cmsfree}, which is generally costly
to maintain especially for small scientific communities with limited
funding and staffing.

The workflow for uploading benchmark results relies on third party
tools using the following steps, illustrated in
Figure~\ref{fig:pfhub_website}.
\begin{itemize}
  \item The users are first required to upload simulation outputs to
    an archival resource (\emph{e.g.},
    Figshare~\cite{figshare}~\footnote{Certain commercial equipment,
      instruments, or materials (or suppliers, or software, ...) are
      identified in this paper to foster understanding. Such
      identification does not imply recommendation or endorsement by
      the National Institute of Standards and Technology, nor does it
      imply that the materials or equipment identified are necessarily
      the best available for the purpose.\label{disclaimer}})
    configured with permissive cross-origin resource sharing (CORS).
  \item The metadata summarizing each simulation is entered into a
    form on the website, including relevant details such as memory
    usage, run time and links to the data archived in the first step.
  \item Upon submission, the Staticman app~\cite{staticman} submits
    the entered metadata as a GitHub pull request to the PFHub GitHub
    repository.  The metadata is stored in a YAML file with a unique
    path in the repository.
  \item Travis CI~\cite{travis} performs linting on the submission and
    then launches a temporary version of the proposed website using
    Surge~\cite{surge}. The PFHub admins can then examine the new
    submission and further changes can be made if necessary.
  \item Once review has been completed to the satisfaction of both the
    uploading scientist and the website maintainers, the pull request
    is merged and served to the World Wide Web using a hosting service
    compatible with GitHub Pages.
\end{itemize}
A combination of Jekyll templates and CoffeeScript are used to access
and download the data links in the submitted YAML files and then
display the data in interactive plots on the website. The interactive
plots are displayed using the Plotly JavaScript Graphing
Library~\cite{plotly} as it provides a programmable interface and
requires minimal configuration.

The current deployment of PFHub has benchmark specifications
consisting of equations, narrative, plots and code samples, and are
composed in Jupyter Notebooks. The Jupyter Notebooks are included as
static objects in the website after translation into HTML using the
nbconvert tool~\cite{jupyter}. There are currently 7 benchmark
problems each with a number of variations. At the time of writing
there are 108 separate benchmark result uploads~\cite{pfhub}, which
have all been approved via pull-request for compatibility with the
website.

@@

The framework has a fully automated test recipe deployed on Travis CI
with an environment built using the Nix Package Manager~\cite{nix}. A
fully automated test environment using continuous integration allows
all developers and users to have common feedback on code updates and
determine the compatibility of result uploads with the deployed
website. The environment is pinned to a specific version of the
Nixpkgs repository ensuring fully reproducible build and test phases
as well as ensuring that the development and automated testing
environments are identical. The full test recipe is outlined in a
\texttt{.travis.yml} file stored in the repository~\cite{travisyml}
and consists of the following steps.

\begin{itemize}
  \item Build the Nix environment from a cached storage reducing the
    build time.
  \item Run automated tests on Jupyter Notebooks using
    NBval~\cite{nbval} and Py.test~\cite{pytest}.
  \item Run validation tests on HTML files using
    HTMLProofer~\cite{htmlproofer}.
  \item Lint and test front-end CoffeeScript using appropriate tools.
  \item Display a temporary version of the website using
    Surge~\cite{surge} for visual review.
\end{itemize}

@@

The PFHub framework can be deployed on any platform supporting Nix,
which includes all contemporary Linux and Mac OS X platforms. Since
the framework is built with Jekyll and automated front-end processing,
it can be deployed on GitHub's Pages infrastructure, which enables
streamlined deployment without the need for any back-end
infrastructure and, thus, largely platform independent. For
development purposes, a Nix installation is required or use of the
supplied Docker container if using Windows.

@@

The PFHub framework can be readily adopted by other communities that
want to follow a CMS-free philosophy and use well supported external
services. The website infrastructure can be cloned as a Git repository
or downloaded as a ZIP archive and deployed with minimum effort. The
mechanism for uploading data using Staticman can be easily configured
for a new repository location. However, customizing the content of the
website for a particular scientific community would require
considerable effort. The following steps are the more challenging
aspects of deploying the framework for a new community.

@@

D.W. wishes to acknowledge the Materials Genome Initiative funding
allocated to the National Institute of Standards and Technology. S.J.D
wishes to acknowledge funding from the U.S. Department of Energy,
Office of Basic Energy Sciences, Division of Materials Sciences and
Engineering under Award \#DE-SC0008637 as part of the Center for
PRedictive Integrated Structural Materials Science (PRISMS Center) at
University of Michigan. PWV is grateful for the financial assistance
under the award 70NANB14H012 from the National Institute of Standards
and Technology as part of the Center for Hierarchical Materials Design
(CHiMaD).

>>>>

PFHub is a community effort spearheaded by the Center for Hierarchical
Materials Design at Northwestern University and the National Institute
of Standards and Technology in support of phase-field code
development. The current PFHub deployment~\cite{pfhub} focuses on
improving cross-collaboration between phase-field code developers and
practitioners by providing a standardized set of benchmark
problems~\cite{bm1, bm2} and a workflow for uploading and comparing
benchmark results from different phase-field codes (\emph{e.g.},
FiPy~\cite{fipy}, MMSP~\cite{mmsp}, MOOSE~\cite{moose},
PRISMS-PF~\cite{prisms-pf}).

@@

The PFHub framework provides a template for other small scientific
communities to host custom content and integrate data from members of
their community. The current deployment provides a facility for
uploading, displaying and comparing results from benchmark problems
supporting phase-field code developers and practitioners. However, the
framework and overall philosophy are broadly transferable to other
communities with some custom configuration and content generation. The
framework uses the Jekyll static website generator~\cite{jekyll} along
with automated front-end processing to eliminate the need for a
CMS~\cite{cmsfree}, which is generally costly to maintain especially
for small scientific communities with limited funding and staffing.
The framework relies on the API, WebSocket and webhook infrastructure
that underpins the modern web and allows external services to have
full-duplex communication between servers and browsers. In particular,
PFHub relies on GitHub's well maintained API and webhook functionality
for external services (such as Travis CI~\cite{travis} and
Staticman~\cite{staticman}).

The workflow for uploading benchmark results relies on third party
tools using the following steps, illustrated in
Figure~\ref{fig:pfhub_website}.
\begin{enumerate}
  \item The users are first required to upload simulation outputs to
    an archival resource (\emph{e.g.}, Figshare\footnote{Certain
      commercial equipment, instruments, or materials (or suppliers,
      or software, ...) are identified in this paper to foster
      understanding. Such identification does not imply recommendation
      or endorsement by the National Institute of Standards and
      Technology, nor does it imply that the materials or equipment
      identified are necessarily the best available for the
      purpose.\label{disclaimer}}~\cite{figshare}) configured with
    permissive cross-origin resource sharing (CORS).
  \item The metadata summarizing each simulation is entered into a
    form on the website, including relevant details such as memory
    usage, run time and links to the data archived in the first step.
  \item Upon submission, the Staticman app~\cite{staticman} submits
    the entered metadata as a pull request aagainst the PFHub
    repository hosted by GitHub. The metadata is stored in a YAML file
    with a unique path in the repository.
  \item Travis CI~\cite{travis} performs linting on the submission and
    then launches a temporary version of the proposed website using
    Surge~\cite{surge}. The PFHub admins can then examine the new
    submission and further changes can be made if necessary.
  \item Once review has been completed to the satisfaction of both the
    uploading scientist and the website maintainers, the pull request
    is merged and served to the World Wide Web using a hosting service
    compatible with GitHub Pages.
\end{enumerate}
A combination of Jekyll templates and CoffeeScript are used to access
and download the data links in the submitted YAML files and then
display the data in interactive plots on the website. The interactive
plots are displayed using the Plotly JavaScript Graphing
Library~\cite{plotly} as it provides a programmable interface and
requires minimal configuration.

The current deployment of PFHub has benchmark specifications
consisting of equations, narrative, plots and code samples, and are
composed in Jupyter Notebooks. The Jupyter Notebooks are included as
static objects in the website after translation into HTML using the
nbconvert tool~\cite{jupyter}. There are currently 7 benchmark
problems each with a number of variations. At the time of writing
there are 108 separate benchmark result uploads~\cite{pfhub} submitted
as pull requests and approved following code review to ensure
compatibility with the website.

@@

The framework has a fully automated test recipe deployed on Travis CI
with an environment built using the Nix Package Manager~\cite{nix}. A
fully automated test environment using continuous integration allows
all developers and users to have common feedback on code updates and
determine the compatibility of result uploads with the deployed
website. The environment is pinned to a specific version of the Nix
Packages Collection (Nixpkgs~\cite{nixpkgs}), ensuring fully
reproducible build and test phases as well as ensuring that the
development and automated testing environments are identical. The full
test recipe is outlined in a YAML file, \texttt{.travis.yml}, file
stored in the repository~\cite{travisyml} and consists of the
following steps.

\begin{enumerate}
  \item Build the Nix environment from a persistent cache on Travis
    CI, reducing the build time.
  \item Run automated tests on Jupyter Notebooks using
    NBval~\cite{nbval} and Py.test~\cite{pytest}.
  \item Run validation tests on HTML files using
    HTMLProofer~\cite{htmlproofer}.
  \item Lint and test front-end CoffeeScript using appropriate tools.
  \item Display a temporary version of the website using
    Surge~\cite{surge} for visual review.
\end{enumerate}

@@

The PFHub framework can be deployed on any platform supporting Nix,
which includes all contemporary Linux and Mac OS X platforms. Since
the framework is built with Jekyll and automated front-end processing,
it can be deployed on GitHub's Pages infrastructure, which enables
streamlined deployment without the need for any back-end
infrastructure and, thus, is largely platform independent. For
development purposes, a local installation of either Nix (on Linux or
Mac) or Docker (on Linux, Mac or Windows) is required.

@@

The PFHub framework can be readily adopted by other communities that
want to follow a CMS-free philosophy and use well supported external
services. The website infrastructure can be cloned as a Git repository
or downloaded as a ZIP archive and deployed with minimum effort. The
mechanism for uploading data using Staticman can be easily configured
for a new repository location. However, customizing the content of the
website for a particular scientific community would require
considerable effort. The current effort is closely integrated with
GitHub, but future deployments could be modified to use other
repository services such as GitLab or BitBucket.

The following steps are the more challenging
aspects of deploying the framework for a new community.

@@

D.W. wishes to acknowledge the Materials Genome Initiative funding
allocated to the National Institute of Standards and Technology. S.J.D
wishes to acknowledge funding from the U.S. Department of Energy,
Office of Basic Energy Sciences, Division of Materials Sciences and
Engineering under Award \#DE-SC0008637 as part of the Center for
PRedictive Integrated Structural Materials Science (PRISMS Center) at
University of Michigan. P.W.V. is grateful for the financial
assistance under the award 70NANB14H012 from the National Institute of
Standards and Technology as part of the Center for Hierarchical
Materials Design (CHiMaD).
